---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# portedcmsy

A minimal and functional port of [cmsy](https://github.com/SISTA16/cmsy). Only the catch-only version of CMSY is supported (not the BSM version).  The only difference between the original CMSY and this ported version is that the internal Schaefer model has been replaced with a c++ version to speed things up.

**this package should not be used for assessment or practical use in any fishery. it is purely for demonstration purposes**

```{r}

# setup -------------------------------------------------------------------
library(tidyverse)

library(R2jags)  # Interface with JAGS

library(coda)

library(parallel)

library(foreach)

library(doParallel)

library(gplots)

library(mvtnorm)

library(snpar)

library(knitr)

library(tinytex)

library(here)

library(portedcmsy)

set.seed(84)

FullSchaefer <-
  F    # initialize variable; automatically set to TRUE if enough abundance data are available

n.chains     <- 4

ncores_for_computation <-
  8 # cores to be used for parallel processing of CMSY

cl  <- makeCluster(ncores_for_computation)

registerDoParallel(cl, cores = ncores_for_computation)

catch_file  <-
  "Stocks_Catch_EU_1.csv" #  name of file containing "Stock", "yr", "ct", and optional "bt"
id_file     <-
  "Stocks_ID_EU_8.csv" #  name of file containing stock-specific info and settings for the analysis
outfile     <-
  paste("Out_", format(Sys.Date(), format = "%B%d%Y_"), id_file, sep = "") # default name for output file

# stock_name <- "smn-dp"
stock_name <- "fle-2732" #
stock_name <- "cod-rock"

cdat <-
  read.csv(
    here("cmsy", catch_file),
    header = T,
    dec = ".",
    stringsAsFactors = FALSE
  ) %>%
  janitor::clean_names()

cinfo <-
  read.csv(
    here("cmsy", id_file),
    header = T,
    dec = ".",
    stringsAsFactors = FALSE
  ) %>%
  janitor::clean_names()

cdat <- cdat %>%
  filter(stock == stock_name)

cinfo <- cinfo %>%
  filter(stock == stock_name)

set.seed(42)
a <- Sys.time()
ported_cmsy <- portedcmsy::funct_cmsy(catches = cdat$ct / 1000,
                          catch_years = cdat$yr,
                          stock = cinfo$stock,
                          common_name = cinfo$name,
                          scientific_name = cinfo$scientific_name,
                          r.low = cinfo$r_low,
                          r.hi = cinfo$r_hi,
                          res = cinfo$resilience,
                          stb.low = cinfo$stb_low,
                          stb.hi = cinfo$stb_hi,
                          int.yr = cinfo$int_yr,
                          intb.low = cinfo$intb_low,
                          intb.hi = cinfo$intb_hi,
                          endb.low = cinfo$endb_low,
                          endb.hi = cinfo$endb_hi,
                          start.yr = min(cdat$yr),
                          end.yr = cinfo$end_year,
                          cores = 12)
port_time <- Sys.time() - a

write_rds(ported_cmsy, "ported_cmsy.rds")
# rm(SchaeferParallelSearch)
a <- Sys.time()

source(here("cmsy","functional-cmsy-2019-9f.R"))

cmsy_time <- Sys.time() - a

message(glue::glue("ported version of cmsy runs {round(as.numeric(port_time)/as.numeric(cmsy_time))} times faster than official cmsy"))

sista_output <-  output %>%
  mutate(b_bmsy = bt / bmsy) %>%
  select(ct, b_bmsy, f_fmsy, year) %>%
  mutate(year = as.numeric(year) - 1 + 1950) %>%
  mutate(code = "SISTA16 CMSY") %>%
  filter(year %in% ported_cmsy$year)


ported_output <- ported_cmsy %>%
  mutate(b_bmsy = bt / bmsy) %>%
  select(ct, b_bmsy, f_fmsy, year) %>%
  mutate(code = "ported CMSY")

compare_outputs <- sista_output %>%
  bind_rows(ported_output) %>%
  group_by(code) %>%
  pivot_longer(c(-code,-year), names_to = "variable", values_to = "value")

compare_outputs %>%
  # filter(year >= 2000) %>%
  ggplot(aes(year, value, color = code, linetype = code)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y") +
  scale_y_continuous(limits = c(0,NA)) +
  scale_color_discrete(labels = c("Ported CMSY", "Official CMSY")) +
  scale_linetype(labels = c("Ported CMSY", "Official CMSY"))


```

